\chapter{Overall Description} \label{chap2}

\section{Product Perspective}
The product is supposed to be an application with a web version and a mobile ones, that simplify the access of the users to the service and is integrated with an other existing system which guarantee a fairy management of the taxi queue. That application will have an internal interface for developers to enable the possibility of adding features.

\section{User Characteristics}
It is considered that the user do have the basic knowledge of operating the internet and to have access to it.

\section{Constraints}
\subsection{Regulatory Policies}
The system should only collects and process raw location information for the scopes related to the specific service provided (creating routes, monitor the distribution of the taxicabs, estimate arriving times, calculating fees). All the personal information should be automatically managed by the system and not shown to any developer or system administrator. All data about location should be aggregated by the system only for statistical purposes. 
Any other relevant data needed for the optimal behavior of the entire system should be collected, used and managed automatically by the system itself according to all the existing privacy laws and regulations.  

\subsection{Hardware Limitations}
The application should be able to receive data from the GPS receiver using its specific communication protocol via Bluetooth interface. 

\section{Assumptions and Dependencies} \label{assump}
\begin{itemize}
	\item [\textbf{A01}]: Given the collected data about the distribution and the total number of the taxicabs, we assume that the coverage of the taxicabs among the zones is almost uniform; therefore the probability of having an empty queue is reasonably low.
	\item [\textbf{A02}]: Given the collected data about the acceptance rate of the taxi drivers, we assume that the probability of reaching the end of the queue without any acceptance is reasonably low.
	\item [\textbf{A03}]: We assume that the maximum number of people sharing the same ride is 3.
	\item [\textbf{A04}]: We assume that the taxi driver will correctly follow the optimal route suggested by the system.
\end{itemize}