\chapter{Scenario Identifying} \label{chap4}

\section{Scenario 1}
Visitor V wants to sign up into the system as a Passenger V opens the mobile or the web app and he/she is immediately asked to Log In or Sign Up. V clicks on the button "Sign Up" and is brought to the registration interface. He/She inserts the desired Username, Password and Email address and selects "Passenger" as type of user. Then V clicks on the button "Register" and, if the credentials are correct, he/she receives a confirmation message. The Passenger Home Page now appears on the app.

\section{Scenario 2}
Passenger A requires a standard ride R and driver D accepts A clicks on the "Request" tab from the Passenger Home Page and the request interface appears on the app. A inserts the destination for his/her desired ride and doesn't check the enable sharing option, then clicks on the button "Request". D receives the incoming request sent by A and decides to accept the call. D receives a message with a summary of R, including indication for an optimal route, and also A receives a confirmation message with information about the taxicab ID of D and the estimated waiting time. 

\section{Scenario 3}
Passenger A reserves a standard ride R. Taxi Driver D1 decline the call but second Taxi Driver D2 accepts
A clicks on the "Reserve" tab from the Passenger Home Page and the reservation interface appears on the app. A inserts the origin, the destination, the desired time for R and doesn't check the enable sharing option, then clicks on the button "Reserve". D1 receives the incoming reservation sent by A and decides to decline the call, so the reservation is sent to D2, that decides to accept the call. D2 receives a message with a summary of R, including indication for an optimal route, and also A receives a confirmation message with information about the taxicab ID of D2.

\section{Scenario 4}
Passenger A1 requires shared ride and another Passenger A2 is added to the same ride. The Taxi Driver D accepts A1 clicks on the "Request" tab from the Passenger Home Page and the request interface appears on the app. A1 inserts the destination for his/her desired ride and checks the enable sharing option, then clicks on the button "Request". A2 does the same thing and, because they are in the same zone and they are going in the same direction, they are put together in the same ride. D receives the incoming request sent by A1 and A2 and decides to accept the call. D receives a message with a summary of R, including indication for an optimal route and the number of passengers, and also A1 and A2 receive a confirmation message with information about the taxicab ID of D the estimated waiting time and the total number of passengers.

\section{Scenario 5}
After a ride, Passenger A wants to see the receipt A has just completed the ride that he/she requested. A opens the app and, after logging in, clicks on the "All Receipts" tab. A list of all his/her receipts appears in the app ordered from the most recent to the oldest. A clicks on the first receipt, which is the one that corresponds to the just completed ride, and sees all the details of the receipt.

\section{Scenario 6}
A Developer D access the app to introduce modifications to the system D opens the mobile or the web app and he/she is immediately asked to Log In or Sign Up. D clicks on the button "Log In" and inserts his/her credentials. If the credentials are correct, D has access to a specific interface dedicated to developers. D introduces modifications to the system and, after checking that everything is correct, submits the modifications. The app restarts and the new modifications are applied. D logs in again and verifies that everything works correctly.
