\chapter{Project Risks} \label{chap5}
Given the nature of the project and the small dimension of the group of developers (3 person), the major risks are related to the availability of all the members of the team and to the respect of the time schedules. In fact, every member of the team has the same importance and has more or less the same skills of the other, so it's not possible to fully replace one team member in a short time, and it's also difficult for the two remaining members to carry out the scheduled tasks efficiently, in case of illness or unavailability of the third member.
Also from the small number of developers depend all the possible risks related to unexpected modifications to the design of the system or also to the scheduling. The lack of hierarchy and the uniformity of skills lead to a necessity of continuous meetings and sharing of ideas and works. All this leads to small reactivity to changes and longer development time.
One possible idea for solving or preventing such problems is to enlarge the team or at least to involve other people in some of the aspect of the project, and try to make all the documentation as much complete and effective as possible, so to make easier and faster for a new member the ingress in the team and the understanding of what's going on.
Another possible idea is to better organize the distribution of the tasks in the team, trying to reach an optimal balance between collaboration and individual work. Trying to enforce collaboration only on the fundamental tasks and enforce decoupling on all the other minor tasks.
